%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  \label{def:definition_1}
  \textit{Definition of a range scan captured from a conventional 2D LIDAR
  sensor.} A conventional 2D LIDAR sensor provides a finite number of ranges,
  i.e. distances to objects within its range, on a horizontal cross-section of
  its environment, at regular angular and temporal intervals, over a defined
  angular range \cite{lidar}. We define a range scan $\mathcal{S}$, consisting
  of $N_s$ rays over an angular range $\lambda$, to be an ordered map
  $\mathcal{S} : \Theta \rightarrow \mathbb{R}_{\geq 0}$, where $\Theta =
  \{\theta_n \in [-\frac{\lambda}{2}, +\frac{\lambda}{2}) : \theta_n =
  -\frac{\lambda}{2} + \lambda \frac{n}{N_s}$, $n = 0,1,\dots, N_s$$-$$1$$\}$.
  Angles $\theta_n$ are expressed relative to the sensor's heading, in the
  sensor's frame of reference.
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  A LIDAR sensor's angle increment $\gamma$ is the angular distance between two
  consecutive rays: $\gamma \triangleq \dfrac{\lambda}{N_s}$
\end{definition}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  \label{def:definition_2}
  \textit{Scan-matching (or scan-to-scan matching) using a 2D LIDAR sensor} (adapted for use in
  two dimensions from \cite{plicp}).
  Let two range scans as defined by Definition \ref{def:definition_1},
  $\mathcal{S}_R$ and $\mathcal{S}_V$, be captured from a LIDAR
  sensor operating in the same environment at both capturing times. Let
  $\bm{p}_V(x_V,y_V,\theta_V)$ be the pose from
  which the sensor captured $\mathcal{S}_V$, expressed in some coordinate
  system (usually a past pose estimate of the sensor). The objective of
  scan-matching in two dimensions is to find the roto-translation
  $\bm{q} = (\bm{t}, \theta)$, $\bm{t} = (\Delta x, \Delta y)$ that minimises
  the distance of the endpoints of $\mathcal{S}_V$ roto-translated by
  $\bm{q}$ to their projection on $\mathcal{S}_R$. Denoting the
  endpoints of $\mathcal{S}_V$ by $\{\bm{p}_V^i\}$, in formula:
  \begin{align}
    \underset{\bm{q}}{\min} \sum\limits_i \Big\| \bm{p}_V^i \oplus \bm{q} - \prod \{ \mathcal{S}_R, \bm{p}_V^i \oplus \bm{q} \}\Big\|^2
    \label{eq:s2sm_def}
  \end{align}
  The symbol ``$\oplus$" denotes the roto-translation operator
  $\bm{p}_V^i \oplus (\bm{t}, \theta) \triangleq \bm{R}(\theta) \bm{p}^i_V + \bm{t}$,
  where $\bm{R}(\theta)$ is the 2D rotation matrix for argument angle $\theta$,
  and $\prod\{\mathcal{S}_R, \bm{p}_V^i \oplus \bm{q} \}$ denotes
  the Euclidean projector on $\mathcal{S}_R$.
\end{definition}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{remark}
  Scan-matching is employed in robotics as a means to odometry,
  primarily in non-wheeled robots where no encoders can be utilised, or as a
  useful ameliorator of the ever-drifting encoder-ed odometry: scans captured at
  consecutive time instances, inputted to a scan-matching algorithm, convey an
  estimate as to the pose of the scan sensor at the second capture time
  relative to that captured first. Scan-matching is being successfully employed
  in the tasks of simultaneous localisation and mapping
  \cite{am_odom_1}-\cite{am_odom_3}, local map construction
  \cite{am_odom_4}-\cite{am_odom_6}, and in people-tracking systems
  \cite{am_odom_7}.
\end{remark}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{definition}
  \label{def:definition_3}
  \textit{Definition of a map-scan.}
  A map-scan is a virtual scan that encapsulates the same pieces of information
  as a scan derived from a physical sensor. Only their underlying operating
  principle is different due to the fact the map-scan refers to distances to
  obstacles within the map ---hence its virtuality. A map-scan is captured from
  a virtual sensor and derived by means of locating intersections of rays
  emanating from the estimate of the sensor's pose and boundaries demarcating
  obstacles in the map.
\end{definition}
