Problem \ref{prob:the_problem} is iteratively decomposed into two disjunctive
sub-problems. The first is estimating the relative orientation of
$\mathcal{S}_1$ with respect to $\mathcal{S}_0$ under the assumption that both
are captured from the same location (subsection
\ref{subsec:method_orientation_correction}). In order to do so, $\mathcal{S}_0$ is
first transformed into a point-set (the map) by projection to the 2D plane. A
number of map-scans are then captured from the projection origin, at
consecutive angular intervals. The intervals' sizes are smaller than the
sensor's angle increment in order for the magnitude of the angular
approximation error to be lower than the angle increment.  The map-scans are
then compared against $\mathcal{S}_1$ for similarity in the POMF matching
sense. The output is an orientation difference estimate between each map-scan
and $\mathcal{S}_1$. In order to increase discernibility between the least
erroneous orientation estimate and the other estimates, the pose estimate is
updated with each orientation estimate, and given over to the translation
correction system, whose resulting location error is proportional to a
pose's orientation error, for one iteration. The similarity between map-scans
captured from these estimates within the map and $\mathcal{S}_1$ is captured in
a per-ray range error metric. The final orientation estimate of $\mathcal{S}_1$
is that of the pose estimate whose map-scan scores the lowest error according
to this metric.

The second sub-problem is estimating the relative translational displacement of
$\mathcal{S}_1$ with respect to $\mathcal{S}_0$ under the assumption that both
are captured from poses of the same orientation (subsection
\ref{subsec:method_location_correction}). The solution is given via
scan-to-map-scan matching by transforming $\mathcal{S}_0$ to a point-set, and
matching map-scans, derived from the pose estimate of $\mathcal{S}_1$ within
the point-set, to $\mathcal{S}_1$ itself. The matching between the two is
derived from first principles given the scans' periodicity and homorientedness;
it is facilitated by iteratively updating the position estimate by a vector
which is a function of the first term of the DFT of the difference between
$\mathcal{S}_1$ and map-scans derived from the point-set of $\mathcal{S}_0$
\cite{Filotheou2022}.

In order to solve the joint problem of estimation of position and orientation,
these two methods are then joined in tandem in an iterative process (subsection
\ref{subsec:method_pose_correction}). At each step the angular intervals at
which map-scans are captured in the orientation correction process are
progressively shortened. This facilitates finer angular and positional
approximation of the sensor's true pose.

\subsection{Estimation of Relative Orientation}
  \label{subsec:method_orientation_correction}
  \input{./sections/04.the_method/subsections/01.orientation_correction.tex}

\subsection{Estimation of Relative Location}
  \label{subsec:method_location_correction}
  \input{./sections/04.the_method/subsections/02.location_correction.tex}

\subsection{Joint Estimation of Relative Orientation and Location}
  \label{subsec:method_pose_correction}
  \input{./sections/04.the_method/subsections/03.pose_correction.tex}
