Scan-matching with the use of a 2D LIDAR sensor began with Iterative Dual
Correspondences (IDC) \cite{LuMilios},
an algorithm incorporating elements of the Iterative Closest Point (ICP)
algorithm \cite{ICP}. The latter and its variants, e.g.
\cite{weighted}-\cite{fgicp}, have become the de facto scan-matching algorithms
in 2D and 3D settings, with research using ICP being still ongoing
\cite{ICP_var_1}-\cite{vgicp}. In particular, PL-ICP \cite{plicp} has been
widely adopted due to its increased accuracy among ICP variants, and the
availability of its source code. ICP and its variants, however, exhibit varying
performance \cite{icp_comp_trade}, limited by the noise level in the input
scans, the choice of prior, and the configuration of the parameters
governing their response. The vast majority of all matching methods adopt ICP's
approach of establishing correspondences between the two input scans, using
various mechanisms, assumptions, and types of sources (e.g. features instead
of points; a detailed review of scan-matching methods may be found in
\cite{pose_selection}). The major problem with establishing correspondences is
that the process becomes more inefficient and error-prone as measurement noise
increases.

By contrast, the method introduced in this paper does not operate by
establishing correspondences. Its rotational component is most akin to those of
\cite{Heng} and \cite{Jiang}. They use Phase-Only Matched Filtering (POMF)
\cite{fmt2d} in both rotation and translation components; the former in one
dimension and the latter in two dimensions. In the latter, the requirements for
a real-time solution and adequate accuracy cannot be fulfilled simultaneously
due to the inability to balance high grid resolution (and therefore high
accuracy) with regular sensor updates. The former alleviates this limitation by
operating in one dimension, but suffers from the same causes, namely,
discretisation errors. Whereas the latter is dependent on the grid's
resolution, the former is dependent on the sensor's immutable angle increment.
In both methods, both the rotational and translational components are affected,
but no mitigation technique is employed to decrease the errors of either their
components. By contrast, the method introduced in this paper addresses all the
above issues by (a) aiming to extricate the orientation error from the
sensor's angle increment, (b) employing a continuous-space translation method,
and (c) fulfilling the real-timeness constraint.
